### 2017-09-18 manuscript/agg-intro.tex
previous work

@@

@@

 * Although several equivalent methods for computing aggregated LCI and/or LCIA results have been described in the literature (Suh 2005; Lenzen 2007), the computational representation of product system models, and the generation of aggregated results, remains steadfastly software-specific.

  - Because the representation of product system models is software-specific, it is also not generally possible to recreate a product system modeled in one software system in a separate software system.

>>>>

What is the point of the new paper?

@@

 * A common theme in all these controversies is the inability for authors and their readers to formally agree on the structure and content of the product system model.

 * Although the general structure for life cycle assessment can be formally stated, there is no current practice for formally describing the product system model and thus, no formal mechanisms for interpretation or review of published LCA studies.

or for distinguishing between the foreground and the background of a model.

@@

 * Although several equivalent methods for computing aggregated LCI and/or LCIA results have been described in the literature (Suh 2005; Lenzen 2007), the computational representation of product system models, and the generation of aggregated results, remains software-specific.

 * Because of the nature of the computation, it is straightforward to provide varying degrees of

The aim of this paper is to present a consistent and reproducible formulation of LCA foreground models, and to focus on the aggregation step
